Curriculum and Imitation Learning for Biped Locomotion on Rough Terrain

### 2019-01-31 paper/rss/main.tex
Move paper to RSS format

\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{amsfonts}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\usepackage[round]{natbib}

\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother

\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\sep}{sep}
\lstset{frame=tb,
  language=Python,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{red},
  stringstyle=\color{red},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\fig}[1]{\includegraphics[width=0.48\textwidth]{#1}}
\newcommand{\figb}[1]{\includegraphics[width=0.95\textwidth]{#1}}
\newcommand{\figz}[1]{\includegraphics[width=0.23\textwidth]{#1.png}}
\newcommand{\m}[1]{\mathbf{#1}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\TT}{\mathcal{T}}

\newcommand{\nhatch}[1]{{\leavevmode\color{magenta} Nathan: #1}}

\usepackage{fancyhdr}
\pagestyle{fancy}

\title{Curriculum and Imitation Learning for Biped Locomotion on Rough Terrain}
\author{TBD}

@@

@@

@@

\begin{table}
  \caption{Parameters of the trajectory generator.
  Note that \texttt{stance\_hip\_roll} is used only in 3D, and \texttt{swing\_knee} is used only in 2D (since in 3D we don't attempt environments with stairs).}
  \label{table:params}
  \hrule
  \begin{tabular}{ll}
    \texttt{toe\_off\_ankle} & Angle for swing ankle during TOE-OFF state (saggital plane). \\
    \texttt{down\_gain} & Gain on distance from target used to trigger the end of the UP state. \\
    \texttt{swing\_hip} & Angle for swing hip during UP state (saggital plane). \\
    \texttt{swing\_knee} & Angle for swing knee during UP state (saggital plane). \\
    \texttt{stance\_hip\_roll} & Angle for stance hip during all three states (coronal plane). \\
  \end{tabular}
  \hrule
\end{table}

@@

\begin{figure}
  \includegraphics[width=0.48\textwidth]{2D_ep.png}
  \includegraphics[width=0.48\textwidth]{3D_ep.png}
  \caption{Screenshots of example episodes.\label{fig:example episodes}}
\end{figure}

@@

\bibliographystyle{plainnat}
\bibliography{bib}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{times}

% numbers option provides compact numerical references in the text. 
\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}
\usepackage{xcolor}
\usepackage{graphicx}

\pdfinfo{
   /Author (Homer Simpson)
   /Title  (Robots: Our new overlords)
   /CreationDate (D:20101201120000)
   /Subject (Robots)
   /Keywords (Robots;Overlords)
}
\newcommand{\nhatch}[1]{{\leavevmode\color{magenta} Nathan: #1}}

@@

\title{Curriculum and Imitation Learning for Biped Locomotion on Rough Terrain}

% You will get a Paper-ID when submitting a pdf file to the conference system
\author{Author Names Omitted for Anonymous Review.}

%\author{\authorblockN{Michael Shell}
%\authorblockA{School of Electrical and\\Computer Engineering\\
%Georgia Institute of Technology\\
%Atlanta, Georgia 30332--0250\\
%Email: mshell@ece.gatech.edu}
%\and
%\authorblockN{Homer Simpson}
%\authorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\authorblockN{James Kirk\\ and Montgomery Scott}
%\authorblockA{Starfleet Academy\\
%San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}}

% avoiding spaces at the end of the author lines is not a problem with
% conference papers because we don't use \thanks or \IEEEmembership

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\authorblockN{Michael Shell\authorrefmark{1},
%Homer Simpson\authorrefmark{2},
%James Kirk\authorrefmark{3}, 
%Montgomery Scott\authorrefmark{3} and
%Eldon Tyrell\authorrefmark{4}}
%\authorblockA{\authorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: mshell@ece.gatech.edu}
%\authorblockA{\authorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\authorblockA{\authorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\authorblockA{\authorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

@@

\begin{abstract}
The abstract goes here.
\end{abstract}

\IEEEpeerreviewmaketitle

@@

\begin{table*}
  \caption{Parameters of the trajectory generator.
  Note that \texttt{stance\_hip\_roll} is used only in 3D, and \texttt{swing\_knee} is used only in 2D (since in 3D we don't attempt environments with stairs).}
  \label{table:params}
  \hrule
  \begin{tabular}{ll}
    \texttt{toe\_off\_ankle} & Angle for swing ankle during TOE-OFF state (saggital plane). \\
    \texttt{down\_gain} & Gain on distance from target used to trigger the end of the UP state. \\
    \texttt{swing\_hip} & Angle for swing hip during UP state (saggital plane). \\
    \texttt{swing\_knee} & Angle for swing knee during UP state (saggital plane). \\
    \texttt{stance\_hip\_roll} & Angle for stance hip during all three states (coronal plane). \\
  \end{tabular}
  \hrule
\end{table*}

@@

\begin{figure}
  \includegraphics[width=0.48\textwidth]{../figures/2D_ep.png}
  \includegraphics[width=0.48\textwidth]{../figures/3D_ep.png}
  \caption{Screenshots of example episodes.\label{fig:example episodes}}
\end{figure}

@@

%\section*{Acknowledgments}

\bibliographystyle{plainnat}
\bibliography{../bib}
